Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber{}}}

### 2018-02-05 Paper.tex
Replace _(\\mathbf\{[:alnum:]+\}) with _{$1}
...using Libre Open Office with regular expressions ticked as an option.

\subsubsection{Transaction Receipt}\linkdest{Transaction_Receipt}{}

@@

\linkdest{transaction_receipt_R}{}\linkdest{tx_receipt_gas_used_R__u}{}The transaction receipt, $R$, is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_{\mathrm{u}}$, the set of logs created through execution of the transaction, \hyperlink{RLP_serialisation_of_a_sequence_of_other_items_R__l_math_def}{$R_{\mathbf{l}}$} and the Bloom filter composed from information in those logs, \hyperlink{RLP_serialisation_of_a_byte_array_R__b_math_def}{$R_{\mathrm{b}}$} and the status code of the transaction, $R_{\mathrm{z}}$:
\begin{equation}
R \equiv (R_{\mathrm{u}}, R_{\mathrm{b}}, R_{\mathbf{l}}, R_{\mathrm{z}})
\end{equation}

@@

Thus $\boldsymbol{\sigma}'$ is the post-transactional state. We also define $\Upsilon^{\mathrm{g}}$ to evaluate to the amount of gas used in the execution of a transaction, $\Upsilon^{\mathbf{l}}$ to evaluate to the transaction's accrued log items and $\Upsilon^{\mathrm{z}}$ to evaluate to the status code resulting from the transaction. These will be formally defined later.

@@

\hypertarget{tx_total_gas_used_Upsilon_pow_g}{}\hypertarget{tx_logs_Upsilon_pow_l}{}\hypertarget{tx_status_Upsilon_pow_z}{}And finally, we specify $\Upsilon^{\mathrm{g}}$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^{\mathrm{z}}$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^{\mathrm{g}}(\boldsymbol{\sigma}, T) & \equiv & T_{\mathrm{g}} - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_{\mathbf{l}} \\
\Upsilon^{\mathrm{z}}(\boldsymbol{\sigma}, T) & \equiv & z
\end{eqnarray}

These are used to help define the \hyperlink{Transaction_Receipt}{transaction receipt}.

@@

In the case of $B_{\mathbf{R}}[n]_{\mathrm{u}}$, we take a similar approach defining each item as the gas used in evaluating the corresponding transaction summed with the previous item (or zero, if it is the first), giving us a running total:
\begin{equation}
\mathbf{R}[n]_{\mathrm{u}} = \begin{cases} 0 & \text{if} \quad n < 0 \\
\begin{array}[b]{l}
\Upsilon^{\mathrm{g}}(\boldsymbol{\sigma}[n - 1], B_{\mathbf{T}}[n])\\ \quad + \mathbf{R}[n-1]_{\mathrm{u}}
\end{array}
 & \text{otherwise} \end{cases}
\end{equation}

For $\mathbf{R}[n]_{\mathbf{l}}$, we utilise the $\Upsilon^\mathbf{l}$ function that we conveniently defined in the transaction execution function.
\begin{equation}
\mathbf{R}[n]_{\mathbf{l}} =
\Upsilon^{\mathbf{l}}(\boldsymbol{\sigma}[n - 1], B_{\mathbf{T}}[n])
\end{equation}

We define $\mathbf{R}[n]_{\mathrm{z}}$ in a similar manner.
\begin{equation}
\mathbf{R}[n]_{\mathrm{z}} =
\Upsilon^{\mathrm{z}}(\boldsymbol{\sigma}[n - 1], B_{\mathbf{T}}[n])
\end{equation}

@@

\min\{ L(\boldsymbol{\mu}_{\mathrm{g}} - C_{\text{\tiny EXTRA}}(\boldsymbol{\sigma}, \boldsymbol{\mu})), \boldsymbol{\mu}_{\mathbf{s}}[0] \} & \text{if} \quad \boldsymbol{\mu}_{\mathrm{g}} \ge C_{\text{\tiny EXTRA}}(\boldsymbol{\sigma}, \boldsymbol{\mu})\\\boldsymbol{\mu}_{\mathbf{s}}[0] & \text{otherwise}

>>>>

\subsubsection{Transaction Receipt}\linkdest{Transaction Receipt}{}

@@

\linkdest{transaction_receipt_R}{}\linkdest{tx_receipt_gas_used_R__u}{}The transaction receipt is a tuple of four items comprising the cumulative gas used in the block containing the transaction receipt as of immediately after the transaction has happened, $R_{\mathrm{u}}$, the set of logs created through execution of the transaction, $R_{\mathbf{l}}$ and the Bloom filter composed from information in those logs, $R_{\mathrm{b}}$ and the status code of the transaction, $R_{\mathrm{z}}$:
\begin{equation}
R \equiv (R_{\mathrm{u}}, R_{\mathrm{b}}, R_{\mathbf{l}}, R_{\mathrm{z}})
\end{equation}

@@

Thus $\boldsymbol{\sigma}'$ is the post-transactional state. We also define $\Upsilon^g$ to evaluate to the amount of gas used in the execution of a transaction, $\Upsilon^\mathbf{l}$ to evaluate to the transaction's accrued log items and $\Upsilon^z$ to evaluate to the status code resulting from the transaction. These will be formally defined later.

@@

\hypertarget{tx_total_gas_used_Upsilon_pow_g}{}\hypertarget{tx_logs_Upsilon_pow_l}{}\hypertarget{tx_status_Upsilon_pow_s}{}And finally, we specify $\Upsilon^g$, the total gas used in this transaction, $\Upsilon^\mathbf{l}$, the logs created by this transaction and $\Upsilon^z$, the status code of this transaction:
\begin{eqnarray}
\Upsilon^g(\boldsymbol{\sigma}, T) & \equiv & T_{\mathrm{g}} - g' \\
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}, T) & \equiv & A_{\mathbf{l}} \\
\Upsilon^z(\boldsymbol{\sigma}, T) & \equiv & z
\end{eqnarray}

These are used to help define the transaction receipt, discussed later.

@@

In the case of $B_{\mathbf{R}}[n]_{\mathrm{u}}$, we take a similar approach defining each item as the gas used in evaluating the corresponding transaction summed with the previous item (or zero, if it is the first), giving us a running total:
\begin{equation}
\mathbf{R}[n]_{\mathrm{u}} = \begin{cases} 0 & \text{if} \quad n < 0 \\
\begin{array}[b]{l}
\Upsilon^g(\boldsymbol{\sigma}[n - 1], B_{\mathbf{T}}[n])\\ \quad + \mathbf{R}[n-1]_{\mathrm{u}}
\end{array}
 & \text{otherwise} \end{cases}
\end{equation}

For $\mathbf{R}[n]_{\mathbf{l}}$, we utilise the $\Upsilon^\mathbf{l}$ function that we conveniently defined in the transaction execution function.
\begin{equation}
\mathbf{R}[n]_{\mathbf{l}} =
\Upsilon^\mathbf{l}(\boldsymbol{\sigma}[n - 1], B_{\mathbf{T}}[n])
\end{equation}

We define $\mathbf{R}[n]_{\mathrm{z}}$ in a similar manner.
\begin{equation}
\mathbf{R}[n]_{\mathrm{z}} =
\Upsilon^z(\boldsymbol{\sigma}[n - 1], B_{\mathbf{T}}[n])
\end{equation}

@@

\min\{ L(\boldsymbol{\mu}_{\mathrm{g}} - C_{\text{\tiny EXTRA}}(\boldsymbol{\sigma}, \boldsymbol{\mu})), \boldsymbol{\mu}_{\mathbf{s}}[0] \} & \text{if} \quad \boldsymbol{\mu}_{\mathrm{g}} \ge C_{\text{\tiny EXTRA}}(\boldsymbol{\sigma}, \boldsymbol{\mu})\\
\boldsymbol{\mu}_{\mathbf{s}}[0] & \text{otherwise}
